% Filename: Abstract
% Last update: Monday, 11/8/2018 by Ally Warner
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Note the use of the * here to suppress numbering of this section
\section*{Abstract}

In order to conduct non-invasive studies of the brain, scientists must build a realistic head and brain model and simulate electrical activity using EEG recordings. Construction of these models is challenging and time consuming. Availability of datasets to build these models is limited in terms of imaging modalities and gender of the patient. In this paper, we provide a detailed, reproducible head and brain modeling pipeline and a high-resolution, multi-modal, freely available, female dataset which expands the diversity and availability of data in the brain modeling and EEG research area. The modeling pipeline specifically outlines image acquisition, preprocessing, registration, and segmentation; three-dimensional, finite element, tetrahedral mesh generation; EEG simulations; and visualization. The dataset includes both functional and structural imaging as well as EEG recordings from two different net sizes. The results at each stage of the model-building process are also included as well as all necessary components for running simulations and visualizations. The availability of this project will help further neuroscience research by providing a high quality test dataset that can be used for a variety of applications, and a pipeline that may help researchers construct new head models more efficiently.
